The \textit{Kepler} Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-12-05 paper/ms.tex
italics
removed 176209 as an interloper A star

% added by DH
\newcommand{\numax}{\mbox{$\nu_{\rm max}$}\xspace}
\newcommand{\Dnu}{\mbox{$\Delta \nu$}\xspace}
\newcommand{\dnu}{\mbox{$\delta \nu$}\xspace}
\newcommand{\muHz}{\mbox{$\mu$Hz}\xspace}
\newcommand{\teff}{\mbox{$T_{\rm eff}$}\xspace}
\newcommand{\logg}{\mbox{$\log g$}\xspace}
\newcommand{\feh}{\mbox{$\rm{[Fe/H]}$}\xspace}
\newcommand{\msun}{\mbox{$\mathrm{M}_{\sun}$}\xspace}
\newcommand{\rsun}{\mbox{$\mathrm{R}_{\sun}$}\xspace}
\newcommand{\kepler}{\emph{Kepler}\xspace}
\newcommand{\ktwo}{\emph{K2}\xspace}
\newcommand{\hipparcos}{\emph{Hipparcos}\xspace}
\newcommand{\gaia}{\emph{Gaia}\xspace}

@@

\title[The Kepler Smear Campaign]{The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants}

@@

Figure~\ref{hrdiagram} shows these stars on a colour-magnitude diagram using \gaia $Bp-Rp$ and absolute~$G$ magnitudes and \gaia~DR2 calibrated distances \citep{gaiadists}, overlaid on the \kepler sample from the Bedell \url{gaia-kepler.fun} crossmatch. The smear targets in this diagram selected to have higher apparent brightnesses than the general \kepler population, appear also to have higher intrinsic luminosities. While this could simply arise from being selected for their apparent brightness, it is {}worth considering whether this is because of a bias in their parallax measurements. While \gaia parallaxes for very bright stars can be subject to systematic error, we have compared to \emph{Hipparcos} \citep{vanleeuwen07b}, and found close agreement for the brightest stars, with a scatter that increases with magnitude. We therefore suggest that parallax bias is not the reason for the smear sample sitting above the majority of the \kepler sample.

@@

Red clump stars, which burn helium in their cores, can be distinguished from hydrogen-shell burning giants asteroseismologically, via their much higher \emph{g}-mode period spacings \citep{rggmodehelium}. 
The term `red clump' arises from the fact that such stars can have a very narrow range of luminosities, so that they appear as a clump in the HR diagram \citep{2016ARA&A..54...95G}. This property makes them useful standard candles to which distances can be accurately computed from photometry. Red clump stars have been used to calibrate the \gaia survey's parallaxes at long distances \citep{2017A&A...598L...4D,2017MNRAS.471..722H,2018A&A...609A.116R}. \gaia~DR2 parallaxes have a zero-point offset of $\sim 0.03$~mas \citep{gaiadr2parallax}, and hierarchical models of the ensemble of \gaia clump stars can be used to accurately estimate this and thereby improve the accuracy of \gaia distances greater than a few~kpc (Hawkins et al., in prep.).

From inspection of the power spectra, HD~181069, HD~183124, HD~182354, HD~182692, and HD~180658 are seen to be red clump stars. A power spectrum of the best example of these, HD~183124, together with a period \'{e}chelle diagram used to estimate its \emph{g}-mode period spacing, are shown in Figure~\ref{HD_183124}. While precise characterization of these stars is beyond the scope of this paper, they are ideal candidates for anchoring models of the mass and metallicity dependence of red clump properties for calibrating \gaia and other distance measures.

@@

\caption{\label{HD_183124}
Power spectrum (left) and period \'{e}chelle diagram (right) of the solar-like oscillations of the red clump star HD~183124. The modes in the power spectrum used for the period \'{e}chelle diagram are highlighted with blue dots. In the period \'{e}chelle diagram we see the characteristic pattern of `bumped' modes from avoided crossings between the comb of \emph{p}-modes and \emph{g}-mode oscillations with a period spacing of $\Delta \Pi = 300.1~\text{s}$.}
\end{figure*}

>>>>

% added by DH
\newcommand{\numax}{\mbox{$\nu_{\rm max}$}\xspace}
\newcommand{\Dnu}{\mbox{$\Delta \nu$}\xspace}
\newcommand{\dnu}{\mbox{$\delta \nu$}\xspace}
\newcommand{\muHz}{\mbox{$\mu$Hz}\xspace}
\newcommand{\teff}{\mbox{$T_{\rm eff}$}\xspace}
\newcommand{\logg}{\mbox{$\log g$}\xspace}
\newcommand{\feh}{\mbox{$\rm{[Fe/H]}$}\xspace}
\newcommand{\msun}{\mbox{$\mathrm{M}_{\sun}$}\xspace}
\newcommand{\rsun}{\mbox{$\mathrm{R}_{\sun}$}\xspace}
\newcommand{\kepler}{\textit{Kepler}\xspace}
\newcommand{\ktwo}{\textit{K2}\xspace}
\newcommand{\hipparcos}{\textit{Hipparcos}\xspace}
\newcommand{\gaia}{\textit{Gaia}\xspace}

@@

\title[The Kepler Smear Campaign]{The \textit{Kepler} Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants}

@@

Figure~\ref{hrdiagram} shows these stars on a colour-magnitude diagram using \gaia $Bp-Rp$ and absolute~$G$ magnitudes and \gaia~DR2 calibrated distances \citep{gaiadists}, overlaid on the \kepler sample from the Bedell \url{gaia-kepler.fun} crossmatch. The smear targets in this diagram selected to have higher apparent brightnesses than the general \kepler population, appear also to have higher intrinsic luminosities. While this could simply arise from being selected for their apparent brightness, it is {}worth considering whether this is because of a bias in their parallax measurements. While \gaia parallaxes for very bright stars can be subject to systematic error, we have compared to \hipparcos \citep{vanleeuwen07b}, and found close agreement for the brightest stars, with a scatter that increases with magnitude. We therefore suggest that parallax bias is not the reason for the smear sample sitting above the majority of the \kepler sample.

@@

Red clump stars, which burn helium in their cores, can be distinguished from hydrogen-shell burning giants asteroseismologically, via their much higher \textit{g}-mode period spacings \citep{rggmodehelium}. 
The term `red clump' arises from the fact that such stars can have a very narrow range of luminosities, so that they appear as a clump in the HR diagram \citep{2016ARA&A..54...95G}. This property makes them useful standard candles to which distances can be accurately computed from photometry. Red clump stars have been used to calibrate the \gaia survey's parallaxes at long distances \citep{2017A&A...598L...4D,2017MNRAS.471..722H,2018A&A...609A.116R}. \gaia~DR2 parallaxes have a zero-point offset of $\sim 0.03$~mas \citep{gaiadr2parallax}, and hierarchical models of the ensemble of \gaia clump stars can be used to accurately estimate this and thereby improve the accuracy of \gaia distances greater than a few~kpc (Hawkins et al., in prep.).

From inspection of the power spectra, HD~181069, HD~183124, HD~182354, HD~182692, and HD~180658 are seen to be red clump stars. A power spectrum of the best example of these, HD~183124, together with a period \'{e}chelle diagram used to estimate its \textit{g}-mode period spacing, are shown in Figure~\ref{HD_183124}. While precise characterization of these stars is beyond the scope of this paper, they are ideal candidates for anchoring models of the mass and metallicity dependence of red clump properties for calibrating \gaia and other distance measures.

@@

\caption{\label{HD_183124}
Power spectrum (left) and period \'{e}chelle diagram (right) of the solar-like oscillations of the red clump star HD~183124. The modes in the power spectrum used for the period \'{e}chelle diagram are highlighted with blue dots. In the period \'{e}chelle diagram we see the characteristic pattern of `bumped' modes from avoided crossings between the comb of \textit{p}-modes and \textit{g}-mode oscillations with a period spacing of $\Delta \Pi = 300.1~\text{s}$.}
\end{figure*}
